Associations between Chlorophyll \emph{a} and various Microcystin-LR Health Advisory Concentrations

### 2015-09-08 manuscript/manuscript.tex
new render and changed to bootstrapped probs in plots

In the summer of 2014, the city of Toledo, OH was forced to shut down
their municipal water supply due in part to an excess of Microcystin-LR
that resulted from a ongoing cyanobacterial harmful algal bloom (cHAB)
in Lake Erie. Since this event, signficant legislation has been passed
in the United States and the US Environmental Protection Agency (USEPA)
has released suggested microcystin-LR concentrations that would trigger
health advisories. While these levels and association advisories are
likey to help mitigate the impacts from harmful algal blooms, they are
not without complications.

One of these complications is that they rely on availble measurments of
Microcysin-LR which requires taking regular water samples and having
those samples process in a lab to determine the toxin concentration
{[}REFS{]}. This has the potentially to be costly and time consuming
both factors which could limit monitoring efforts. Fortunately,
microcystin-LR has been shown to be associated with several other, more
easily measured components of water quality.

>>>>

In the summer of 2014, the city of Toledo, OH was forced to shut down
their municipal water supply due in part to an excess of Microcystin-LR
that resulted from a ongoing cyanobacterial harmful algal bloom (cHAB)
in Lake Erie. Since this event, signficant legislation has been passed
in the United States and the US Environmental Protection Agency (USEPA)
has released suggested microcystin-LR concentrations that would trigger
health advisories. While these levels and associated advisories are
likey to help mitigate the impacts from harmful algal blooms, they are
not without complications.\\One of these complications is that they rely
on availble measurments of Microcysin-LR which requires taking regular
water samples and having those samples process in a lab to determine the
toxin concentration {[}REFS{]}. This has the potentially to be costly
and time consuming both factors which could limit monitoring efforts.
Fortunately, microcystin-LR has been shown to be associated with several
other, more easily measured components of water quality.
